Automatic Matching of Bullet Lands

### 2016-01-16 imaging-paper.Rnw
A few minor revisions to new CMS paragraph

Counting the maximal number of CMS is part of current practice to identify bullet matches~\citep{nichols:1997, nichols:2003, nichols:2003b}. 
In the example of Figure~\ref{fig:match}, the number of consecutive matching striations (CMS) is fifteen, a  high number indicative of a match between the bullets. 
\hh{XXX Note that the definition given in this paper does not coincide with the one given in \citet{thompson:2013}. There, CMS is defined only in terms of matching peaks. Additionally, \citet{thompson:2013} peaks are only used, if they can be identified and matched `within a tolerable range' between lands. The definition given in here, is computationally less complex, but should come close in values, because of the requirement to only consider signatures from a stable region in the land. In the Hamby study, the definition of CMS by \citet{thompson:2013} leads to approximately half of the values of CMS defined in this paper (with a correlation coefficient between the values of the two definitions of about 0.92). XXX}
For lead bullets, such as this, \citet{biasotti:1959} considered four or more consecutive lines to be sufficient evidence of a match. \hh{XXX Biasotti's four or more consecutive lines is closer to eight or more with our definition. Should we just multiply our CMS by 0.5, to account for the fact that between every two peaks has to be a valley? XXX} We will assess this claim in the next section.

>>>>

Counting the maximal number of CMS is part of current practice to identify bullet matches~\citep{nichols:1997, nichols:2003, nichols:2003b}. 
In the example of Figure~\ref{fig:match}, the number of consecutive matching striations (CMS) is fifteen, a  high number indicative of a match between the bullets. 
\hh{XXX Note that the definition given in this paper does not coincide with the one given in \citet{thompson:2013}. There, CMS is defined only in terms of matching peaks. Additionally, \citet{thompson:2013} peaks are only used if they can be identified and matched `within a tolerable range' between lands. The definition given here is computationally less complex, but should yield similar values, because of the requirement to only consider signatures from a stable region in the land. In the Hamby study, the definition of CMS by \citet{thompson:2013} leads to approximately half of the values of CMS defined in this paper (with a correlation coefficient between the values of the two definitions of about 0.92). XXX}
For lead bullets, such as this, \citet{biasotti:1959} considered four or more consecutive lines to be sufficient evidence of a match. \hh{XXX Biasotti's four or more consecutive lines is closer to eight or more with our definition. Should we just multiply our CMS by 0.5, to account for the fact that between every two peaks has to be a valley? XXX} We will assess this claim in the next section.
